---
title: "Operational Workforce Forecasting"
date: 2018-02-18
author: "Paul Forst, Tammy Hang, Rachel Kopecky, Jack Letcher, Ian O'Connor"
output:
  html_document:
    theme: sandstone
    toc: yes
    toc_depth: 4
    toc_float: yes
  html_notebook:
    fig_caption: yes
    highlight: textmate
    theme: sandstone
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r global_options, include = FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

```

```{r include=FALSE}
#   Load Required Packages and Files  
#   Check that necessary packages are installed

packages <- c("tidyverse", "lubridate", "forecast", "tibbletime", "ggplot2", "ggthemes", "stringr", "gridExtra", "fpp", "astsa", "knitr")

new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

#   Load Neccessary Packages
sapply(packages, library, character.only = TRUE)
```


# Problem Definition

* Help forecast staffing needs based on the growth and seasonal trends of the client 
* Understand the potential demands that client sales/clearances have on traffic 


*Approach* 

* Analyze the inbound and outbound loads at the main warehouse 
* Mainly look at a monthly view but also potentially dive down to days of the week to better understand staffing at micro level 
* While inbound and outbound are highly(?) correlated, there are some differences that could potentially be used to save on resource costs 

 
*Goals* 

* Allow better management and staffing practices to increase productivity and reduce costs 
* Increase the bottom line 


# Exploration

```{r}
inbound <- read.csv("Inbound Data.csv")
outbound <- read.csv("Outbound Data.csv")

#Convert Date to proper date class
inbound$Date <- mdy(inbound$Date)
outbound$Date <- mdy(outbound$Date)

#correction for comma in a Dollars field
inbound$Dollars <- str_replace(inbound$Dollars, ',', "")
outbound$Dollars <- str_replace(outbound$Dollars, ',', "")

#Convert Dollars and Wage to numeric
inbound$Dollars <- as.numeric(sub('\\$','',as.character(inbound$Dollars))) 
outbound$Dollars <- as.numeric(sub('\\$','',as.character(outbound$Dollars)))
inbound$Wage <- as.numeric(sub('\\$','',as.character(inbound$Wage))) 
outbound$Dollars <- as.numeric(sub('\\$','',as.character(outbound$Wage)))

#Order by Date
inbound <- inbound[order(inbound$Date), ]
outbound <- outbound[order(outbound$Date), ]

all <- rbind(inbound, outbound)

#Use tibble time to convert the data frames to time series
inbound <- as_tbl_time(inbound, Date) %>% 
  group_by(Report.Location)
outbound <- as_tbl_time(outbound, Date) %>% 
  group_by(Report.Location)
all <- as_tbl_time(all, Date) %>% 
  group_by(Report.Location)

#Aggregate to location and day level to first plot
# inbound_summary_monthly <- inbound %>% 
#   dplyr::arrange(Report.Location, Date) %>% 
#   dplyr::mutate(Date = collapse_index(Date, "monthly")) %>% 
#   dplyr::group_by(Report.Location, Date, add = TRUE) %>% 
#   dplyr::summarise(ttl_hrs = sum(Hours), 
#                    ttl_pay = sum(Dollars), 
#                    median_wage = median(Wage))

summary_monthly <- all %>% 
  dplyr::arrange(Report.Location, Date) %>% 
  dplyr::mutate(Date = collapse_index(Date, "monthly")) %>% 
  dplyr::group_by(Dept, Report.Location, Date, add = TRUE) %>% 
  dplyr::mutate(num = length(unique(Badge))) %>% 
  dplyr::summarise(ttl_hrs = sum(Hours), 
                   ttl_pay = sum(Dollars), 
                   median_wage = median(as.numeric(Wage)),
                   num = sum(num))



summary_quarterly <- all %>% 
  dplyr::arrange(Report.Location, Date) %>% 
  dplyr::mutate(Date = collapse_index(Date, "quarterly")) %>% 
  dplyr::group_by(Dept, Report.Location, Date, add = TRUE) %>% 
  dplyr::summarise(ttl_hrs = sum(Hours), 
                   ttl_pay = sum(Dollars), 
                   median_wage = median(as.numeric(Wage)))


# inbound_summary_quarterly <- inbound %>% 
#   dplyr::arrange(Report.Location, Date) %>% 
#   dplyr::mutate(Date = collapse_index(Date, "quarterly")) %>% 
#   dplyr::group_by(Report.Location, Date, add = TRUE) %>% 
#   dplyr::summarise(ttl_hrs = sum(Hours), 
#                    ttl_pay = sum(Dollars), 
#                    median_wage = median(Wage))

Sys.setenv(TZ = 'America/Louisville')

all$Date <- as.POSIXct(all$Date, tz = 'America/Louisville')

# inbound_summary_weekly <- inbound %>% 
#   dplyr::arrange(Report.Location, Date) %>% 
#   dplyr::mutate(Date = collapse_index(Date, "weekly")) %>% 
#   dplyr::group_by(Report.Location, Date, add = TRUE) %>% 
#   dplyr::summarise(ttl_hrs = sum(Hours), 
#                    ttl_pay = sum(Dollars), 
#                    median_wage = median(Wage))

summary_weekly <- all %>% 
  dplyr::arrange(Report.Location, Date) %>% 
  dplyr::mutate(Date = collapse_index(Date, "weekly")) %>% 
  dplyr::group_by(Dept, Report.Location, Date, add = TRUE) %>% 
  dplyr::mutate(num = length(unique(Badge))) %>% 
  dplyr::summarise(ttl_hrs = sum(Hours), 
                   ttl_pay = sum(Dollars), 
                   median_wage = median(as.numeric(Wage)),
                   num = sum(num))



```

The plots below display the total pay and total hours for both inbound and outbound production at three different locations.

```{r}

p1 <- summary_quarterly %>% 
  ggplot(aes(Date, 
             ttl_pay)) +
  geom_line(aes(color = Report.Location, linetype = Dept)) +
  scale_y_continuous(labels = scales::dollar) +
  theme_tufte() +
  ggtitle("Total Pay by Quarter") +
  ylab("Total Pay") +
  theme(axis.title.x = element_blank()) 

p2 <- summary_monthly %>% 
  ggplot(aes(Date, 
             ttl_pay)) +
  geom_line(aes(color = Report.Location, linetype = Dept)) +
  scale_y_continuous(labels = scales::dollar) +
  theme_tufte() +
  ggtitle("Total Pay by Month") +
  ylab("Total Pay") +
  theme(axis.title.x = element_blank(), legend.position = "none")

p3 <- summary_weekly %>% 
  ggplot(aes(Date, 
             ttl_pay)) +
  geom_line(aes(color = Report.Location, linetype = Dept)) +
  scale_y_continuous(labels = scales::dollar) +
  theme_tufte() +
  ggtitle("Total Pay by Week") +
  ylab("Total Pay") +
  theme(axis.title.x = element_blank(), legend.position = "none")

grid.arrange(p1, p2, p3, nrow = 3)

```

We notice that there is some seasonality in the data, as Q4 of each year appears to see a spike in both inbound and outbound production. We also notice that there is a slight upward trend in the data over time, which is likely due to acquisitions that have taken place over this period. 

```{r}

p4 <- summary_quarterly %>% 
  ggplot(aes(Date, 
             ttl_hrs)) +
  geom_line(aes(color = Report.Location, linetype = Dept)) +
  scale_y_continuous() +
  theme_tufte() +
  ggtitle("Total Hours by Quarter") +
  ylab("Total Hours") +
  theme(axis.title.x = element_blank())

p5 <- summary_monthly %>% 
  ggplot(aes(Date, 
             ttl_hrs)) +
  geom_line(aes(color = Report.Location, linetype = Dept)) +
  scale_y_continuous() +
  theme_tufte() +
  ggtitle("Total Hours by Month") +
  ylab("Total Hours") +
  theme(axis.title.x = element_blank(), legend.position = "none")


p6 <- summary_weekly %>% 
  ggplot(aes(Date, 
             ttl_hrs)) +
  geom_line(aes(color = Report.Location, linetype = Dept)) +
  scale_y_continuous() +
  theme_tufte() +
  ggtitle("Total Hours by Week") +
  ylab("Total Hours") +
  theme(axis.title.x = element_blank(), legend.position = "none")

grid.arrange(p4, p5, p6, nrow = 3)

```

As there is incomplete data for the *RW* and *IC Finance-Lou locations*, for the analysis that follows we are going to focus solely on the inbound and outbound data for the ***LOU*** location.

## Decomposition

### Inbound

```{r fig.width = 10}

#Need to decompose and plot
#Start with monthly inbound data at the LOU location
inbound_summary_monthly_hrs_ts <- summary_monthly %>%
  filter(Report.Location == "LOU" & Dept == "Inbound")  %>% 
  ungroup() %>% 
  select(ttl_hrs)

inbound_summary_monthly_pay_ts <- summary_monthly %>%
  filter(Report.Location == "LOU" & Dept == "Inbound")  %>% 
  ungroup() %>% 
  select(ttl_pay)

# convert data frame to time series object
inbound_summary_monthly_hrs_ts <- ts(data = inbound_summary_monthly_hrs_ts, start = c(2015,1), frequency = 12)
inbound_summary_monthly_pay_ts <- ts(data = inbound_summary_monthly_pay_ts, start = c(2015,1), frequency = 12)

# str(inbound_summary_ts)

d1<- autoplot(decompose(inbound_summary_monthly_hrs_ts), main = "Total Hours per Month (Additive Decomp)")
#plot(decompose(inbound_summary_monthly_hrs_ts, type = "multiplicative"))

d2 <- autoplot(decompose(inbound_summary_monthly_pay_ts), main = "Total Pay per Month (Additive Decomp)")
#plot(decompose(inbound_summary_monthly_pay_ts, type = "multiplicative"))


grid.arrange(d1,d2, ncol = 2)

```

After looking at the decomposition of the monthly inbound series for both hours and pay, it appears that both of these can be described by an additive model, as the variation in the random component appears to be roughly constant over time.


### Outbound
```{r fig.width = 12, fig.height = 9}

#Need to decompose and plot
#Start with monthly inbound data at the LOU location
outbound_summary_monthly_hrs_ts <- summary_monthly %>%
  filter(Report.Location == "LOU" & Dept == "Outbound")  %>% 
  ungroup() %>% 
  select(ttl_hrs)

outbound_summary_monthly_pay_ts <- summary_monthly %>%
  filter(Report.Location == "LOU" & Dept == "Outbound")  %>% 
  ungroup() %>% 
  select(ttl_pay)

# convert data frame to time series object
outbound_summary_monthly_hrs_ts <- ts(data = outbound_summary_monthly_hrs_ts, start = c(2015,1), frequency = 12)
outbound_summary_monthly_pay_ts <- ts(data = outbound_summary_monthly_pay_ts, start = c(2015,1), frequency = 12)

layout(matrix(c(1,1,2,2), 2, 2, byrow = TRUE))

# str(inbound_summary_ts)
d5 <- autoplot(decompose(outbound_summary_monthly_hrs_ts), main = "Total Hours per Month (Additive Decomp)")

d6 <- autoplot(decompose(outbound_summary_monthly_hrs_ts, type = "multiplicative"), main = "Total Hours per Month (Multiplicative Decomp)")
outbound_monthly_decomp_hrs <- decompose(outbound_summary_monthly_hrs_ts, type = "multiplicative")

d7 <- autoplot(decompose(outbound_summary_monthly_pay_ts), main = "Total Pay per Month (Additive Decomp)")

d8 <- autoplot(decompose(outbound_summary_monthly_pay_ts, type = "multiplicative"), main = "Total Pay per Month (Multiplicative Decomp)")
outbound_monthly_decomp_pay <- decompose(outbound_summary_monthly_pay_ts, type = "multiplicative")

grid.arrange(d5, d6, d7, d8, nrow = 2, ncol = 2)
```

The variation in the random component of the monthly outbound series does not appear to be constant, so we will need to use a multiplicative decomposition for this series.

## Comparing Trends

Here we compare the trend components of the different series.

```{r}

plot(decompose(inbound_summary_monthly_hrs_ts)$trend, ylim = c(0,20000), col = "green", type = "p", main = "Total Hours per Month, Inbound vs Outbound Trend", sub = "Red Line - Outbound, Green Dot - Inbound", ylab = "Total Hours");  lines(decompose(outbound_summary_monthly_hrs_ts)$trend, col = "red")
```

```{r}
plot(decompose(outbound_summary_monthly_pay_ts)$trend, ylim = c(2000, 125000), col = "green", type = "p", main = "Total Pay per Month, Inbound vs Outbound Trend", sub = "Red Line - Outbound, Green Dot - Inbound", ylab = "Total Pay");
lines(decompose(inbound_summary_monthly_pay_ts)$trend, col = "red")
```

We notice that both the inbound and outbound series have an increasing trend for both total hours and total pay. The outbound series (red) appears to be increasing at a faster rate.

#Forecasting

## Mean

Although the mean will not provide us with an accurate forecast for these particular series, we began with this method because we wanted to get an understanding of what the forecast would look like if we just take the mean of the historic data.

```{r fig.width = 12, fig.height = 9}

m1 <- autoplot(meanf(inbound_summary_monthly_hrs_ts, h = 24), main = "Inbound, Total Hours per Month", ylab = "Total Hours")

m2 <- autoplot(meanf(inbound_summary_monthly_pay_ts, h = 24), main = "Inbound, Total Pay per Month", ylab = "Total Pay")

m3 <- autoplot(meanf(outbound_summary_monthly_hrs_ts, h = 24), main = "Outbound, Total Hours per Month", ylab = "Total Hours")

m4 <- autoplot(meanf(outbound_summary_monthly_pay_ts, h = 24), main = "Outbound, Total Pay per Month", ylab = "Total Pay")

grid.arrange(m1, m2, m3, m4, nrow = 2, ncol = 2)
```

As expected, these forecasts are not good, as they do not account for any of the seasonality or trend that we have seen in the past.

## Random Walk 

We then wanted to understand what the forecast would look like if we attempt to predict the *change* that occurs from one period to the next, rather than trying to predict the actual values. This is where Random Walk forecasting comes in. At each time period, the value takes a random step away from its previous position.  

```{r}

r1 <- autoplot(rwf(inbound_summary_monthly_hrs_ts, h = 24, drift = F), main = "Random Walk, Monthly Hours", ylab = "Total Hours") 
r2 <- autoplot(rwf(inbound_summary_monthly_hrs_ts, h = 24, drift = T), main = "Random Walk with Drift, Monthly Hours", ylab = "Total Hours")

r3 <- autoplot(rwf(inbound_summary_monthly_pay_ts, h = 24, drift = F), main = "Random Walk, Monthly Pay", ylab = "Total Pay")
r4 <- autoplot(rwf(inbound_summary_monthly_pay_ts, h = 24, drift = T), main = "Random Walk with Drift, Monthly Pay", ylab = "Total Pay")

r5 <- autoplot(rwf(outbound_summary_monthly_hrs_ts, h = 24, drift = F), main = "Random Walk, Monthly Hours", ylab = "Total Hours")
r6 <- autoplot(rwf(outbound_summary_monthly_hrs_ts, h = 24, drift = T), main = "Random Walk with Drift, Monthly Hours", ylab = "Total Hours")

r7 <- autoplot(rwf(outbound_summary_monthly_pay_ts, h = 24, drift = F), main = "Random Walk, Monthly Pay", ylab = "Total Pay")
r8 <- autoplot(rwf(outbound_summary_monthly_pay_ts, h = 24, drift = T), main = "Random Walk with Drift, Monthly Pay", ylab = "Total Pay")

```

### Inbound

```{r fig.width = 12, fig.height = 9}
grid.arrange(r1, r2, r3, r4, nrow = 2, ncol = 2)
```

For a Random Walk without drift, the mean of the steps will be zero, while a Ranom Walk with Drift will have a nonzero mean, and will better emphasize any trend that we see in the data.

### Outbound

```{r fig.width = 12, fig.height = 9}
grid.arrange(r5, r6, r7, r8, nrow = 2, ncol = 2)
```

The Random Walk without Drift is equivalent to a Naive Forecasting method, which just forecasts a value equal to the last one observed.

## Seasonal Naive

While a Naive forecasting method forecasts a value equal to the one last observed, a Seasonal Naive method accounts for seasonality in the data by forecasting a value equal to the last value from the same season. As we saw in the decomp above, the variation in the seasonal component was relatively constant, so this method would provide us a forecast that expects that trend to continue.

### Inbound
```{r fig.width=12, fig.height=9}
s1 <- autoplot(snaive(inbound_summary_monthly_hrs_ts, h = 24), main = "Inbound, Total Hours per Month", ylab = "Total Hours")

s2 <- autoplot(snaive(inbound_summary_monthly_pay_ts, h = 24), main = "Inbound, Total Pay per Month", ylab = "Total Pay")

grid.arrange(s1, s2, nrow = 2)
```

This method provides us with a seasonal forecast without overcompensating for the slight upward trend that we see near the end of 2017, as we will soon see is not the case with some of the other forecasting methods.

### Outbound
```{r}
s3 <- autoplot(snaive(outbound_summary_monthly_hrs_ts, h = 24), main = "Outbound, Total Hours per Month", ylab = "Total Hours")

s4 <- autoplot(snaive(outbound_summary_monthly_pay_ts, h = 24), main = "Outbound, Total Pay per Month", ylab = "Total Pay")

grid.arrange(s3, s4, nrow = 2)
```

## Holt-Winters Exponential Smoothing

We also used the Holt-Winters method for exponential smoothing, in order to better identify the patterns in the trend and seasonal components of the data by smoothing out some of the noise.

#### Inbound

Based on the decompositions from above, for the inbound series, we will need use the Holt-Winters seasonal *additive* method, as the variation in the seasonal component of the series appear to be constant.

```{r}
# Hours
inbound_monthly_hrs_HW <- HoltWinters(inbound_summary_monthly_hrs_ts, seasonal = "additive")
hw1 <- autoplot(forecast(inbound_monthly_hrs_HW, h = 24), main = "Holt-Winters Forecast, Inbound Monthly Hours", ylab = "Total Hours")

inbound_monthly_pay_HoltWinters <- HoltWinters(inbound_summary_monthly_pay_ts, seasonal = "additive")
hw2 <- autoplot(forecast(inbound_monthly_pay_HoltWinters, h = 24), main = "Holt-Winters Forecast, Inbound Monthly Pay", ylab = "Total Pay")

grid.arrange(hw1, hw2, nrow = 2)
```

Based on the Holt-Winters forecast for our monthly series, both our inbound hours and pay are expected to continue to increase heavily through 2018. These forecasts seem to really capitalize on the upward trend that we see toward the end of 2017, which may not lend an accurate forecast.

#### Outbound

The variation in the seasonal component of the outbound series were relatively constant as well, so we will again use the *additive* method.

```{r}
# Monthly
# Hours

outbound_monthly_hrs_HW <- HoltWinters(outbound_summary_monthly_hrs_ts, seasonal = "additive")
hw5 <- autoplot(forecast(outbound_monthly_hrs_HW, h = 24), main = "Holt-Winters Forecast, Outbound Monthly Hours", ylab = "Total Hours")

# Pay
outbound_monthly_pay_HoltWinters <- HoltWinters(outbound_summary_monthly_pay_ts, seasonal = "additive")
hw6 <- autoplot(forecast(outbound_monthly_pay_HoltWinters, h = 24), main = "Holt-Winters Forecast, Outbound Monthly Pay", ylab = "Total Pay")

grid.arrange(hw5, hw6, nrow = 2)
```

The forecasts for the outbound series do not appear to provide as drastic of a forecast, as the forecast seems to more closely match the patterns that we have noticed from 2015 to 2017. However, it does still capitalize on the increase in trend at the end of 2017.

<!-- Next we should test if our models are stationary, whether or not autocorrelation exists. If they are non-stationary, then we could possibly improve them using a different technique. -->

<!-- ```{r} -->

<!-- acf(inbound_monthly_hrs_HoltWinters_Forecast$residuals[13:36]) -->
<!-- Box.test(inbound_monthly_hrs_HoltWinters_Forecast$residuals[13:36]) -->
<!-- ``` -->
<!-- ```{r} -->
<!-- acf(inbound_monthly_pay_HoltWinters_Forecast$residuals[13:36]) -->
<!-- Box.test(inbound_monthly_pay_HoltWinters_Forecast$residuals[13:36]) -->
<!-- ``` -->
<!-- ```{r} -->
<!-- acf(inbound_weekly_hrs_HoltWinters_Forecast$residuals[53:156]) -->
<!-- Box.test(inbound_weekly_hrs_HoltWinters_Forecast$residuals[53:156]) -->
<!-- ``` -->
<!-- ```{r} -->
<!-- acf(inbound_weekly_pay_HoltWinters_Forecast$residuals[53:156]) -->
<!-- Box.test(inbound_weekly_pay_HoltWinters_Forecast$residuals[53:156]) -->
<!-- ``` -->

<!-- All of our Holt-Winters models for the inbound series appear to be stationary. -->

## ARIMA

We can sometimes create better forecasts by utilizing ARIMA models. 

#### Inbound

```{r evaluate = FALSE, include = FALSE}
adf.test(inbound_summary_monthly_hrs_ts)
adf.test(inbound_summary_monthly_pay_ts)

```

From the Dickey-Fuller test, we can confirm that neither of the monthly series are stationary. We apply some differencing below:

```{r }
#Montly Hours
df1 <- autoplot(inbound_summary_monthly_hrs_ts, main = "Inbound Hours per Month", ylab = "Total Hours")
inbound_summary_monthly_hrs_ts_Diff <- diff(inbound_summary_monthly_hrs_ts)
df2 <- autoplot(inbound_summary_monthly_hrs_ts_Diff, main = "Inbound Hours per Month, Difference = 1", ylab = "Total Hours")

inbound_summary_monthly_hrs_ts2 <- diff(inbound_summary_monthly_hrs_ts, differences = 2)
df3 <- autoplot(inbound_summary_monthly_hrs_ts2, main = "Inbound Hours per Month, Difference = 2", ylab = "Total Hours")

grid.arrange(df1, df2, df3, nrow = 3)
```

A difference of 2 appears to make the monthly hours series stationary, and we find that this is the case for the monthly pay series as well. We can then begin to build our ARIMA models. We will use the `auto.arima` function that will choose the best ARIMA model to fit to each series.

```{r}
inbound_summary_monthly_hrs_ts_ARIMA <- auto.arima(inbound_summary_monthly_hrs_ts)
inbound_summary_monthly_hrs_ts_forecast <- forecast(inbound_summary_monthly_hrs_ts_ARIMA)
a1 <- autoplot(inbound_summary_monthly_hrs_ts_forecast, main = "ARIMA Forecast, Inbound Monthly Hours", ylab = "Total Hours")

inbound_summary_monthly_pay_ts_ARIMA <- auto.arima(inbound_summary_monthly_pay_ts)
inbound_summary_monthly_pay_ts_forecast <- forecast(inbound_summary_monthly_pay_ts_ARIMA)
a2 <- autoplot(inbound_summary_monthly_pay_ts_forecast, main = "ARIMA Forecast, Inbound Monthly Pay", ylab = "Total Pay")

grid.arrange(a1, a2, nrow = 2)

```

#### Outbound

Next we will use ARIMA to forecast our outbound series.

```{r evaluate = FALSE, include = FALSE}

acf(outbound_summary_monthly_hrs_ts)
acf(outbound_summary_monthly_pay_ts)

```

```{r evaluate = FALSE, include = FALSE}
 adf.test(outbound_summary_monthly_hrs_ts)
 adf.test(outbound_summary_monthly_pay_ts)
```

From the Dickey-Fuller test, we can confirm that the monthly series are not stationary, and We again find that both the monthly hours and pay series can achieve stationarity after two differences.

```{r include = FALSE}

outbound_monthly_hrs_diff1 <- diff(outbound_summary_monthly_hrs_ts, differences = 1)
adf.test(outbound_monthly_hrs_diff1)

outbound_monthly_hrs_diff2 <- diff(outbound_summary_monthly_hrs_ts, differences = 2)
adf.test(outbound_monthly_hrs_diff2)

```

<!-- The monthly hours series achieves stationarity after two differences. We can see below that this is the same for the monthly pay series as well. -->

```{r include = FALSE}

outbound_monthly_pay_diff1 <- diff(outbound_summary_monthly_pay_ts, differences = 1)
adf.test(outbound_monthly_pay_diff1)

outbound_monthly_pay_diff2 <- diff(outbound_summary_monthly_pay_ts, differences = 2)
adf.test(outbound_monthly_pay_diff2)

```

Again we will use `auto.arima` to fit the models.

```{r}
# Outbound ARIMA Models
outbound_summary_monthly_hrs_ts_ARIMA <- auto.arima(outbound_summary_monthly_hrs_ts)
a5 <- autoplot(forecast(outbound_summary_monthly_hrs_ts_ARIMA), main = "ARIMA Forecast, Outbound Monthly Hours", ylab = "Total Hours")

outbound_summary_monthly_pay_ts_ARIMA <- auto.arima(outbound_summary_monthly_pay_ts)
a6 <- autoplot(forecast(outbound_summary_monthly_pay_ts_ARIMA), main = "ARIMA Forecast, Outbound Monthly Pay", ylab = "Total Pay")

grid.arrange(a5, a6, nrow = 2)
```

# Model Evaluation

We can evaluate the different models we built by calculating the Mean Squared Error (MSE) and Mean Absolute Error (MAE) for each. The model that best describes the underlying data will minimize both of these errors.

#### Inbound Monthly Hours

##### Mean Squared Error

```{r}
# Inbound Monthly Hours
ib_mon_hrs_cv_rw <- tsCV(inbound_summary_monthly_hrs_ts, rwf, h = 24, drift = F)
ib_mon_hrs_cv_rwd <- tsCV(inbound_summary_monthly_hrs_ts, rwf, h = 24, drift = T)
ib_mon_hrs_cv_snaive <- tsCV(inbound_summary_monthly_hrs_ts, snaive, h = 24)
ib_mon_hrs_cv_meanf <- tsCV(inbound_summary_monthly_hrs_ts, meanf, h = 24)
ib_mon_hrs_cv_hw <- tsCV(inbound_summary_monthly_hrs_ts, hw, seasonal = "additive")

# MSE
mse1 <- mean(ib_mon_hrs_cv_meanf^2, na.rm = T); mse2 <- mean(ib_mon_hrs_cv_rw^2, na.rm = T); mse3 <- mean(ib_mon_hrs_cv_rwd^2, na.rm = T); mse4 <- mean(ib_mon_hrs_cv_snaive^2, na.rm = T); mse5 <- mean(ib_mon_hrs_cv_hw^2, na.rm = T)

Method <- c("Mean Forecasting", "Random Walk", "Random Walk with Drift", "Seasonal Naive", "Holt-Winters")
MSE <- c(mse1, mse2, mse3, mse4, mse5)
table1 <- data.frame(Method, MSE)
kable(table1, align = c('r', 'r', 'r'))
```

##### Mean Absolute Error

```{r}
# MAE
mae1 <- mean(abs(ib_mon_hrs_cv_meanf), na.rm = T); mae2 <- mean(abs(ib_mon_hrs_cv_rw), na.rm = T); mae3 <- mean(abs(ib_mon_hrs_cv_rwd), na.rm = T); mae4 <- mean(abs(ib_mon_hrs_cv_snaive), na.rm = T); mae5 <- mean(abs(ib_mon_hrs_cv_hw), na.rm = T)

MAE <- c(mae1, mae2, mae3, mae4, mae5)
table2 <- data.frame(Method, MAE)
kable(table2, align = c('r', 'r', 'r'))
```

For the inbound monthly hours series, both the MSE and MAE are minimized under the Holt-Winters method. 

We can evaluate the ARIMA models by analyzing the residuals. From the residual analysis below, we can see that our ARIMA model for this series has relatively normally distributed, indepent residuals.

```{r}
# Residuals
checkresiduals(inbound_summary_monthly_hrs_ts_ARIMA, test = FALSE)
```

```{r include = FALSE}
# Inbound Monthly Pay
ib_mon_pay_cv_rw <- tsCV(inbound_summary_monthly_pay_ts, rwf, h = 24, drift = F)
ib_mon_pay_cv_rwd <- tsCV(inbound_summary_monthly_pay_ts, rwf, h = 24, drift = T)
ib_mon_pay_cv_snaive <- tsCV(inbound_summary_monthly_pay_ts, snaive, h = 24)
ib_mon_pay_cv_meanf <- tsCV(inbound_summary_monthly_pay_ts, meanf, h = 24)
ib_mon_pay_cv_hw <- tsCV(inbound_summary_monthly_pay_ts, hw, seasonal = "additive")

# MSE
mean(ib_mon_pay_cv_meanf^2, na.rm = T); mean(ib_mon_pay_cv_rw^2, na.rm = T); mean(ib_mon_pay_cv_rwd^2, na.rm = T); mean(ib_mon_pay_cv_snaive^2, na.rm = T); mean(ib_mon_pay_cv_hw^2, na.rm = T)

# MAE
mean(abs(ib_mon_pay_cv_meanf), na.rm = T); mean(abs(ib_mon_pay_cv_rw), na.rm = T); mean(abs(ib_mon_pay_cv_rwd), na.rm = T); mean(abs(ib_mon_pay_cv_snaive), na.rm = T); mean(abs(ib_mon_pay_cv_hw), na.rm = T)

# Residuals
checkresiduals(inbound_summary_monthly_pay_ts_ARIMA)
```

```{r include = FALSE}
# Outbound Monthly Hours
ob_mon_hrs_cv_rw <- tsCV(outbound_summary_monthly_hrs_ts, rwf, h = 24, drift = F)
ob_mon_hrs_cv_rwd <- tsCV(outbound_summary_monthly_hrs_ts, rwf, h = 24, drift = T)
ob_mon_hrs_cv_snaive <- tsCV(outbound_summary_monthly_hrs_ts, snaive, h = 24)
ob_mon_hrs_cv_meanf <- tsCV(outbound_summary_monthly_hrs_ts, meanf, h = 24)
ob_mon_hrs_cv_hw <- tsCV(outbound_summary_monthly_hrs_ts, hw, seasonal = "additive")

# MSE
mean(ob_mon_hrs_cv_meanf^2, na.rm = T); mean(ob_mon_hrs_cv_rw^2, na.rm = T); mean(ob_mon_hrs_cv_rwd^2, na.rm = T); mean(ob_mon_hrs_cv_snaive^2, na.rm = T); mean(ob_mon_hrs_cv_hw^2, na.rm = T)

# MAE
mean(abs(ob_mon_hrs_cv_meanf), na.rm = T); mean(abs(ob_mon_hrs_cv_rw), na.rm = T); mean(abs(ob_mon_hrs_cv_rwd), na.rm = T); mean(abs(ob_mon_hrs_cv_snaive), na.rm = T); mean(abs(ob_mon_hrs_cv_hw), na.rm = T)

# Residuals
checkresiduals(outbound_summary_monthly_hrs_ts_ARIMA)
```

```{r include = FALSE}
# Outbound Monthly Pay
ob_mon_pay_cv_rw <- tsCV(outbound_summary_monthly_pay_ts, rwf, h = 24, drift = F)
ob_mon_pay_cv_rwd <- tsCV(outbound_summary_monthly_pay_ts, rwf, h = 24, drift = T)
ob_mon_pay_cv_snaive <- tsCV(outbound_summary_monthly_pay_ts, snaive, h = 24)
ob_mon_pay_cv_meanf <- tsCV(outbound_summary_monthly_pay_ts, meanf, h = 24)
ob_mon_pay_cv_hw <- tsCV(outbound_summary_monthly_pay_ts, hw, seasonal = "additive")

# MSE
mean(ob_mon_pay_cv_meanf^2, na.rm = T); mean(ob_mon_pay_cv_rw^2, na.rm = T); mean(ob_mon_pay_cv_rwd^2, na.rm = T); mean(ob_mon_pay_cv_snaive^2, na.rm = T); mean(ob_mon_pay_cv_hw^2, na.rm = T)

# MAE
mean(abs(ob_mon_pay_cv_meanf), na.rm = T); mean(abs(ob_mon_pay_cv_rw), na.rm = T); mean(abs(ob_mon_pay_cv_rwd), na.rm = T); mean(abs(ob_mon_pay_cv_snaive), na.rm = T); mean(abs(ob_mon_pay_cv_hw), na.rm = T)

# Residuals
checkresiduals(outbound_summary_monthly_pay_ts_ARIMA)
```

Each of our ARIMA models have relatively normally distributed, independent residuals, and the chart below displays the modeling method that minimizes the MSE and MAE for each series:

```{r}
Series <- c("Inbound Monthly Hours", "Inbound Monthly Pay", "Outbound Monthly Hours", "Outbound Monthly Pay")
MSE <- c("Holt-Winters", "Holt-Winters", "Random Walk with Drift", "Random Walk with Drift")
MAE <- c("Holt-Winters", "Holt-Winters", "Random Walk with Drift", "Holt-Winters")

table3 <- data.frame(Series, MSE, MAE)

kable(table3, align = c('r', 'c', 'c'))
```


# Conclusion









\  

\  

\  

\  

\  

\  

\  

\  

# Appendix

## Analysis of Weekly Data

### Decomposition

#### Outbound

```{r fig.width = 10}

#Need to decompose and plot
#Start with monthly inbound data at the LOU location
inbound_summary_weekly_hrs_ts <- summary_weekly %>%
        filter(Report.Location == "LOU" & Dept == "Inbound")  %>% 
        ungroup() %>% 
        select(ttl_hrs)

inbound_summary_weekly_pay_ts <- summary_weekly %>%
        filter(Report.Location == "LOU" & Dept == "Inbound")  %>% 
        ungroup() %>% 
        select(ttl_pay)

# convert data frame to time series object
inbound_summary_weekly_hrs_ts <- ts(data = inbound_summary_weekly_hrs_ts, start = c(2015,1), frequency = 52)
inbound_summary_weekly_pay_ts <- ts(data = inbound_summary_weekly_pay_ts, start = c(2015,1), frequency = 52)

# str(inbound_summary_ts)
d3 <- autoplot(decompose(inbound_summary_weekly_hrs_ts), main = "Total Hours per Week (Additive Decomp)")
#plot(decompose(inbound_summary_weekly_hrs_ts, type = "multiplicative"))

d4 <- autoplot(decompose(inbound_summary_weekly_pay_ts), main = "Total Pay per Week (Additive Decomp)")
#plot(decompose(inbound_summary_weekly_pay_ts, type = "multiplicative"))

grid.arrange(d3, d4, ncol = 2)
```

Again, the decomposition of the inbound weekly series for both hours and pay appear to have roughly constant variation in the random component, and thus an additive decomposition model is sufficient.

#### Outbound

```{r fig.width = 12, fig.height = 9}

#Need to decompose and plot
#Start with monthly inbound data at the LOU location
outbound_summary_weekly_hrs_ts <- summary_weekly %>%
        filter(Report.Location == "LOU" & Dept == "Outbound")  %>% 
        ungroup() %>% 
        select(ttl_hrs)

outbound_summary_weekly_pay_ts <- summary_weekly %>%
        filter(Report.Location == "LOU" & Dept == "Outbound")  %>% 
        ungroup() %>% 
        select(ttl_pay)

# convert data frame to time series object
outbound_summary_weekly_hrs_ts <- ts(data = outbound_summary_weekly_hrs_ts, start = c(2015,1), frequency = 52)
outbound_summary_weekly_pay_ts <- ts(data = outbound_summary_weekly_pay_ts, start = c(2015,1), frequency = 52)

# str(inbound_summary_ts)
d9 <- autoplot(decompose(outbound_summary_weekly_hrs_ts), main = "Total Hours per Week (Additive Decomp)")

d10 <- autoplot(decompose(outbound_summary_weekly_hrs_ts, type = "multiplicative"), main = "Total Hours per Week (Multiplicative Decomp)")
outbound_weekly_decomp_hrs <- decompose(outbound_summary_weekly_hrs_ts, type = "multiplicative")

d11 <- autoplot(decompose(outbound_summary_weekly_pay_ts), main = "Total Pay per Week (Additive Decomp)")

d12 <- autoplot(decompose(outbound_summary_weekly_pay_ts, type = "multiplicative"), main = "Total Pay per Week (Multiplicative Decomp)")
outbound_weekly_decomp_pay <- decompose(outbound_summary_weekly_pay_ts, type = "multiplicative")

grid.arrange(d9,d10,d11,d12, nrow = 2, ncol = 2)
```

Again, the variation in the random component of the weekly outbound series does not appear to be constant, so we will need to use a multiplicative decomposition for this series.


### Forecasting

#### Holt-Winters Exponential Smoothing

##### Inbound

```{r}

inbound_weekly_hrs_HoltWinters <- HoltWinters(inbound_summary_weekly_hrs_ts, seasonal = "additive")
hw3 <- autoplot(forecast(inbound_weekly_hrs_HoltWinters), main = "Holt-Winters Forecast, Inbound Weekly Hours", ylab = "Total Hours")

# Pay
inbound_weekly_pay_HoltWinters <- HoltWinters(inbound_summary_weekly_pay_ts, seasonal = "additive")
hw4 <- autoplot(forecast(inbound_weekly_pay_HoltWinters), main = "Holt-Winters Forecast, Inbound Weekly Pay", ylab = "Total Pay")

grid.arrange(hw3, hw4, nrow = 2)

```
Our Holt-Winters forecasts for the weekly series appear to be lower than those for the monthly series, and they do not increase as dramatically moving into 2018. We will need to further analyze both the series and the forecasts to determine which is closer to what we should expect moving forward.

##### Outbound

```{r}

outbound_weekly_hrs_HoltWinters <- HoltWinters(outbound_summary_weekly_hrs_ts, seasonal = "multiplicative")
hw7 <- autoplot(forecast(outbound_weekly_hrs_HoltWinters), main = "Holt-Winters Forecast, Outbound Weekly Hours", ylab = "Total Hours")

# Pay
outbound_weekly_pay_HoltWinters <- HoltWinters(outbound_summary_weekly_pay_ts, seasonal = "multiplicative")
hw8 <- autoplot(forecast(outbound_weekly_pay_HoltWinters), main = "Holt-Winters Forecast, Outbound Weekly Pay", ylab = "Total Pay")

grid.arrange(hw7, hw8, nrow = 2)

```

#### ARIMA

##### Inbound

```{r}
adf.test(inbound_summary_weekly_hrs_ts)
adf.test(inbound_summary_weekly_pay_ts)

```
From the Dickey-Fuller test, we can confirm that the weekly pay series is stationary, while the weekly hours series is not. The weekly hours series requires 2 differences to achieve stationarity.

```{r}
inbound_summary_weekly_hrs_ts_ARIMA <- auto.arima(inbound_summary_weekly_hrs_ts)
inbound_summary_weekly_hrs_ts_forecast <- forecast(inbound_summary_weekly_hrs_ts_ARIMA)
a3 <- autoplot(inbound_summary_weekly_hrs_ts_forecast, main = "ARIMA Forecast, Inbound Weekly Hours", ylab = "Total Hours")

inbound_summary_weekly_pay_ts_ARIMA <- auto.arima(inbound_summary_weekly_pay_ts)
inbound_summary_weekly_ts_forecast <- forecast(inbound_summary_weekly_pay_ts_ARIMA)
a4 <- autoplot(inbound_summary_weekly_ts_forecast, main = "ARIMA Forecast, Inbound Weekly Pay", ylab = "Total Pay")

grid.arrange(a3, a4, nrow = 2)

```

##### Outbound

Next we will use ARIMA to forecast our outbound series.

```{r evaluate = FALSE, include = FALSE}

acf(outbound_summary_weekly_hrs_ts)
acf(outbound_summary_weekly_pay_ts)

```

```{r evaluate = FALSE, include = FALSE}
adf.test(outbound_summary_weekly_hrs_ts)
adf.test(outbound_summary_weekly_pay_ts)
```

From the Dickey-Fuller test, we can confirm that the weekly series are stationary.

Again we will use `auto.arima` to fit the models.

```{r}
# Outbound ARIMA Models

weekly_hours <- auto.arima(outbound_summary_weekly_hrs_ts)
a7 <- autoplot(forecast(weekly_hours), main = "ARIMA Forecast, Outbound Weekly Hours", ylab = "Total Hours")

weekly_pay <- auto.arima(outbound_summary_weekly_pay_ts)
a8 <- autoplot(forecast(weekly_pay), main = "ARIMA Forecast, Outbound Weekly Pay", ylab = "Total Pay")

grid.arrange(a7, a8, nrow = 2)
```

